|

### 2021-05-20 article/resubmission.Rmd
adds draft of resubmission

[^catarina]: Research Associate, School of International Relations, Fundação Getulio Vargas, <catarinamroman@gmail.com>, <http://catarinaroman.github.io>.

@@

Over the past decades, a large literature has examined the relationship between
legislature size and public expenditure. @weingast1981political provided the
general framework to analyse distributive politics. The authors argue that the
larger the number of legislative districts ($n$), the smaller the share of tax
burden each one will bear ($1/n$), thus legislators have an incentive to
overspend in their districts and transfer the costs to the entire polity. Most
early studies that empirically tested the "law of $1/n$", as the theory is
currently known, indeed found a positive correlation between the number of
legislature seats and different measures of government spending, although the
effect was often limited to one house [e.g., @baqir2002districting;
@gilligan1995deviations; @gilligan2001fiscal]. Recent research has further
questioned the validity of the "law of $1/n$". For instance, spending limits,
bicameralism, or strong executives may reduce the inefficiency of pork barrel
projects [@bradbury2001legislative; @chen_malhotra_2007; @primo2006stop].
Moreover, @primo2008distributive affirm that, due to spatial spillovers, a
collection of small districts can supply public goods more efficiently than the
central government. The authors conclude that a "reverse law of $1/n$" may hold,
wherein a higher number of legislators in small constituencies decrease the
overall public spending.

Our survey of the scholarship confirms this continuum of positive,
insignificant, and negative results. Out of the `r dim(dat)[1]` coefficients
included in our article sample, `r as.numeric(round(prop.table(table(dat$scoefnd))*100, 1)[which(names(prop.table(table(dat$scoefnd)))=='Positive Significant')])`\% of
them are positive and statistically significant, `r as.numeric(round(prop.table(table(dat$scoefnd))*100, 1)[which(names(prop.table(table(dat$scoefnd)))=='Positive Insignificant')])`\%
are positive and statistically insignificant, `r as.numeric(round(prop.table(table(dat$scoefnd))*100, 1)[which(names(prop.table(table(dat$scoefnd)))=='Negative Insignificant')])`\%
are negative and statistically insignificant, and `r as.numeric(round(prop.table(table(dat$scoefnd))*100, 1)[which(names(prop.table(table(dat$scoefnd)))=='Negative Significant')])`\% are
negative and statistically significant. Given this diversity of empirical
findings, a systematic review of the existing evidence may help us reach a
meaningful conclusion about the effect of legislature size on public spending.
Meta-analysis is the most appropriate method for this task. Meta-analysis
combines the outcomes of multiple studies into a single estimation and allows
scholars to draw robust conclusions from the aggregated data
[@cooper2019handbook; @hedges1985statistical]. It can also identify potential
sources of study heterogeneity, enabling researchers to assess threats to
external validity and direct future efforts into more promising areas of
academic inquiry [@doucouliagos2008democracy].

In this letter, we conduct the first meta-analysis that tests the generality of
the "law of $1/n$". We have selected `r length(unique(dat$id))` articles that
use quantitative methods to assess the impact of legislature size over
government spending across several dimensions. We run two sets of models: the
first group uses only the main estimates of each selected paper (`r dim(dat)[1]`),
while the second set includes all coefficients reported in our
sample (`r dim(fulldat)[1]`).\footnote{Although there are `r length(unique(dat$id))`
papers in our review, we include `r dim(dat)[1]` coefficients in the restricted 
sample. This is because `r as.numeric(sum(table(table(dat$id))[-1]))` articles 
report separate estimates for the impact of lower and upper house size on 
government expenditures. In the full model, we add every outcome reported in the 
papers, regardless of whether the coefficient comes from the main tables or from 
robustness checks. We discuss our sampling process in the Methods section and in 
the Supplementary Material.}
Our independent variables consist of three measures, namely the size of the
lower chamber ($n$), its natural logarithm (log($n$)), and the number of members
in the upper chamber ($k$). We evaluate their effect upon public expenditure per
capita, the natural logarithm of public expenditure per capita, and government
expenditure as a percentage of GDP. We then estimate if the results vary
according to four potential sources of effect heterogeneity.

Aggregate results show that legislative size has no significant impact on
public spending. However, the meta-regressions suggest that our study sample
has high levels of heterogeneity, and effects differ substantially according to
study specifications. We find that one reliable predictor of effect size is the
research method employed in the original paper. While papers that employ
conventional linear regressions often find a positive relation between
legislature size and government budgets, recent studies using modern methods of
causal inference, specially those with regression discontinuity designs,
provide consistent evidence for a negative relation. This goes in contrast with
the original theory and supports the existence of a "reverse law of $1/n$".
Additionally, we find that non-majoritarian voting systems decrease government
spending as a percentage of GDP, which is also evidence against the theoretical
expectations of the "law of $1/n$", and they do not have a relevant impact on
the other measures of public expenditure. In summary, our analysis does not
provide robust support for the theory as originally conceived, and causal
inference models suggest that larger legislatures are associated with lower
public spending.

@@

We collected the study sample using three criteria. First, the study should
cite \citet{weingast1981political} as their work is foundational to the
distributive politics literature. Second, the study had to use quantitative
methods to estimate the relationship between our variables of
interest.\footnote{As meta-analysis requires a single estimate per observation,
we excluded articles that use interaction terms or quadratic specifications of
our independent variables.} Third, the study should be written in the English
language. We conducted a primary search using Scopus, Microsoft Academic, and
Google Scholar, three large academic databases.\footnote{See the Supplementary
Material for code.}

After applying our exclusion criteria, the search produced a dataset of 
`r length(unique(dat$id))` studies as of the 21\textsuperscript{st} of November,
2019. Table \ref{tab:papers} contains the full list of articles from which we
drew data. A PRISMA\footnote{The Preferred Reporting Items for Systematic
Reviews and Meta-Analyses (PRISMA) statement provides a checklist designed
to improve the quality and transparency of study selection processes in
meta-analyses. For more information on the PRISMA framework, see
\citet{liberati2009prisma}.} flow diagram showing the number of resulting
papers after each review step is available in the Supplementary Material.

\footnotesize
\begin{longtable}{>{\raggedright\arraybackslash}p{2.9cm}>{\raggedright\arraybackslash}p{4.5cm}>{\centering\arraybackslash}p{1.3cm}>{\centering\arraybackslash}p{1cm}>{\centering\arraybackslash}p{1cm}>{\centering\arraybackslash}p{1.4cm}>{\centering\arraybackslash}p{2.4cm}}
\caption{Papers included in the meta-analysis, ordered by year of appearance}\\
\toprule
\raggedright Author(s) & \centering Title & \centering Journal & \centering Year & \centering Country & \centering Method & \raggedleft Electoral System
\tabularnewline
\midrule
\endhead
```{r, echo = FALSE, results = 'asis', cache = T}
build_nams <- function(x) {
  x_ <- unlist(strsplit(as.character(x), ' & ', fixed = T, useBytes = T))
  if(length(x_) == 1) return(x_)
  else {
    aux <- x_[1]
      for (i in 2:length(x_))
        if (i == length(x_)){
          aux <- paste(aux, ' \\& \\\\ ', x_[i], sep = '')
        } else {
          aux <- paste(aux, ',\\\\ ', x_[i], sep = '')
        }
  }
  return(paste('\\begin{tabular}[t]{@{}l@{}}', aux,'\\end{tabular}', 
                   sep = ''))
}
aux <- dat %>%
  select(authorCite, title, journalCode, year, locationISO, method, elecsys3) %>%
  unique() %>%
  arrange(year)
for (i in 1:dim(aux)[1]) {
  cat(paste(build_nams(aux$authorCite[i]), ' & ', aux$title[i], ' & ',
      aux$journalCode[i], ' & ', aux$year[i], ' & ', 
      aux$locationISO[i], ' & ', aux$method[i], ' & ', 
      aux$elecsys3[i], ' \\\\ [0.5ex]', sep = ''), '\n')
}
```
\bottomrule
\label{tab:papers}
\begin{minipage}{\textwidth}
\renewcommand{\footnoterule}{}
\vspace{-0.5cm}
\footnotetext{\textbf{Note:} Unpub$=$Unpublished, JPE$=$Journal of Political
Economy, EJPE$=$European Journal of Political Economy, PC$=$Public Choice,
JPubE$=$Journal of Public Economics, JPriE$=$Journal of Private Enterprise,
APSR$=$American Political Science Review, SEJ$=$Southern Economic Journal,
UAR$=$Urban Affairs Review, SCID$=$Studies in Comparative International
Development, SSQ$=$Social Science Quarterly, SPPQ$=$State Politics and Policy
Quarterly, CPS$=$Comparative Political Studies, RivPE$=$Rivista di Politica
Economica, E\&P$=$Economics and Politics, NTJ$=$National Tax Journal,
OLS$=$Ordinary least squares, IV$=$Instrumental variables, Panel$=$Panel
data/fixed effects, RDD$=$Regression discontinuity design, M$=$Majoritarian,
NM$=$Non-majoritarian (mixed or proportional representation). Country codes
follow the ISO 3166-1 alpha-3 international standard.} \end{minipage}
\end{longtable}

@@

Regarding the dependent variables included in the sample, `r as.numeric(table(unique(dat[,c('id','depvar2')])$depvar2)[which(names(table(unique(dat[,c('id','depvar2')])$depvar2))=='ExpPC')])` studies employ
public expenditure per capita, `r as.numeric(table(unique(dat[,c('id','depvar2')])$depvar2)[which(names(table(unique(dat[,c('id','depvar2')])$depvar2))=='logExpPC')])` papers use its natural logarithm, and `r as.numeric(table(unique(dat[,c('id','depvar2')])$depvar2)[which(names(table(unique(dat[,c('id','depvar2')])$depvar2))=='PCTGDP')])` of them
analyse the impact of legislature size on public expenditures as a percentage of
GDP. This indicates that the area has refined the original formulation of $1/n$
suggested by \citet{weingast1981political} and tested the impact of larger
legislatures on different measures of government spending. Our independent
variables of interest are $n$, lower chamber size (`r as.numeric(table(dat$indepvar2)[which(names(table(dat$indepvar2))=='N')])`), ($\log(n)$), the natural
logarithm of lower chamber size (`r as.numeric(table(dat$indepvar2)[which(names(table(dat$indepvar2))=='logN')])`), and $k$, which represents upper chamber
size (`r as.numeric(table(dat$indepvar2)[which(names(table(dat$indepvar2))=='K')])`).

We also coded four moderators that may help us understand the heterogeneity in
the reported results. We included them in our meta-regressions alongside an
indicator for the type of independent variable used in the original study ($n$,
log($n$), or $k$). The additional moderators are: 1) publication year; 2) paper
publication in an academic journal; 3) electoral system; 4) estimation method.
Since the literature on the "law of $1/n$" is notably diverse, we were
restricted to include only the moderators that either refer to important
theoretical questions, such as the effect of the electoral system on public
spending, or to essential characteristics of the publications themselves.
Although more moderators exist in the literature (ie., data aggregation level),
they do not appear as often as required for the meta-regressions. Table
\ref{tab:descriptive} shows the descriptive statistics of the moderator
variables.

@@

```{r, echo = FALSE, results='hide', warning=FALSE, message=FALSE}
fulldat$usemeta2 <- factor(fulldat$usemeta)
levels(fulldat$usemeta2) <- c("Other Coefficients", "Main Coefficients")
fulldat$usemeta2 <- as.character(fulldat$usemeta2)
fulldat$usemeta2 <- factor(fulldat$usemeta2)
aux <- select(fulldat, usemeta2, indepvar2, year, published,
              elecsys2, method) %>%
  rename(`Independent Variables` = indepvar2,
         `Year` = year,
         `Published work` = published,
         `Electoral system` = elecsys2,
         `Estimation method` = method)

res <- export2latex(
  descrTable(~.-usemeta2, aux, y = aux$usemeta2,
             show.p.overall = F, show.all = T, all.last = T), 
  caption = 'Descriptive statistics of moderators\\label{tab:descriptive}'
)
res <- gsub(pattern = '\\[ALL\\]', 'All Coefficients', res$desc, useBytes = T)
cat(res)
```

\footnotesize
\begin{longtable}{lccc}\caption{Descriptive Statistics of Moderators\label{tab:descriptive}}\\
\hline  
& Main Coefficients & Other Coefficients &    All Coefficients   \\ 
&       N=42        &       N=100        &    N=142    \\
\hline
\hline     
\endfirsthead 
\multicolumn{4}{l}{\tablename\ \thetable{} \textit{-- continued from previous page}}\\ 
\hline
& Main Coefficients & Other Coefficients &    All Coefficients   \\ 
&       N=42        &       N=100        &    N=142    \\ 
\hline
\hline  
\endhead   
\hline
\multicolumn{4}{l}{\textit{continued on next page}} \\ 
\endfoot   
\multicolumn{4}{l}{}  \\ 
\endlastfoot 
Independent Variables: &                   &                    &            \\ 
$\qquad$K &    12 (28.6\%)     &     33 (33.0\%)     & 45 (31.7\%) \\ 
$\qquad$N &    24 (57.1\%)     &     55 (55.0\%)     & 79 (55.6\%) \\ 
$\qquad$logN &     6 (14.3\%)     &     12 (12.0\%)     & 18 (12.7\%) \\ 
Year &    2009 (6.56)    &    2008 (5.82)     & 2008 (6.04)\\ 
Published work: &                   &                    &            \\ 
$\qquad$Yes &    36 (85.7\%)     &     93 (93.0\%)     & 129 (90.8\%)\\ 
$\qquad$No &     6 (14.3\%)     &     7 (7.00\%)      & 13 (9.15\%) \\ 
Electoral system: &                   &                    &            \\ 
$\qquad$Majoritarian &    22 (52.4\%)     &     46 (46.0\%)     & 68 (47.9\%) \\ 
$\qquad$Non-Majoritarian &    20 (47.6\%)     &     54 (54.0\%)     & 74 (52.1\%) \\ 
Estimation method: &                   &                    &            \\ 
$\qquad$OLS &    11 (26.2\%)     &     36 (36.0\%)     & 47 (33.1\%) \\ 
$\qquad$PANEL &    23 (54.8\%)     &     51 (51.0\%)     & 74 (52.1\%) \\ 
$\qquad$IV &     5 (11.9\%)     &     7 (7.00\%)      & 12 (8.45\%) \\ 
$\qquad$RDD &     3 (7.14\%)     &     6 (6.00\%)      &  9 (6.34\%)  \\

\hline
\end{longtable}

Since most selected articles have more than one effect size, the observations
in our dataset are not independent. To reduce the impact of multicollinearity,
we estimate the models using two sets of study coefficients. The first group
includes only the most rigorous model from each paper, that is, those estimated
with the largest $n$, most control variables, and fixed effects if the authors
added them. If the article employed a regression discontinuity design, we chose
the coefficient from the optimal bandwidth or from the intermediate one. This
sample encompasses `r dim(dat)[1]` estimates, as `r as.numeric(sum(table(table(dat$id))[-1]))` articles analysed two dependent or
independent variables of interest \citep{baqir1999districts, bjedov2014impact,
bradbury2001legislative, chen_malhotra_2007, crowley2019law,
lee2016supermajority, lee2018court, maldonado2013legislatures, primo2006stop,
ricciuti2003trading}. Our second sample, in contrast, contains all the `r dim(fulldat)[1]` effect
sizes reported in the `r length(unique(dat$id))` papers. Here we focus on the results for our restricted
sample as we consider them more robust, but the findings are very similar when
we use the extended set. We discuss eventual differences in the next section.
Please refer to the Supplementary Material for further information about our
sampling process and for the complete results.

@@

The "law of $1/n$" states that more legislators increase government expenditure.
Here we employ three methods to assess the empirical validity of that
relationship. First, we run a binomial one-proportion z-test to determine
whether the study coefficients have a positive or negative sign. Then, we fit 9
random-effect models using the \texttt{meta} \citep{balduzzi2019perform} and the
\texttt{dmetar} \citep{dmetar2019} packages for the \texttt{R} statistical
language \citep{rstats2019}. We estimate the true effect size variance
($\tau^2$) with a Restricted Maximum Likelihood Estimator, which the literature
considers the most precise for continuous dependent variables
\citep{veroniki2016methods}. Lastly, we run a series of meta-regressions to test
possible sources of result heterogeneity. To recapitulate, our independent
variables of interest are lower chamber size ($n$), the natural logarithm of
lower chamber size (log($n$)), and upper chamber size ($k$). The dependent
variables are public expenditure per capita, the natural logarithm of public
expenditure per capita, and government expenditure as a percentage of GDP. Since
the outcomes have different scales, we treat them separately in our models.

@@

The binomial z-test evaluates whether the coefficient of our independent
variables are positive or negative. The null hypothesis here states that the
sign of the coefficient is equally likely to be positive or negative. We start
with $n$, lower house size. Our results indicate that there is no correlation
between the number of legislators in the lower house and public expenditure 
(successes = `r as.numeric(binN$statistic)`, trials = `r as.numeric(binN$parameter)`, p~success~ = `r round(as.numeric(binN$estimate), 3)`, 95\% CI = [`r round(as.numeric(binN$conf.int[1]), 3)`; `r round(as.numeric(binN$conf.int[2]), 3)`],
$p$-value = `r round(as.numeric(binN$p.value), 3)`). Note that the "law of $1/n$" suggests that there is a positive
association between both. The binomial test for log($n$) also shows a
non-statistically significant result (successes = `r as.numeric(binlogN$statistic)`, trials = `r as.numeric(binlogN$parameter)`, p~success~ = `r round(as.numeric(binlogN$estimate), 3)`, 95\% CI = [`r round(as.numeric(binlogN$conf.int[1]), 3)`; `r round(as.numeric(binlogN$conf.int[2]), 3)`],
$p$-value = `r round(as.numeric(binlogN$p.value), 3)`). In contrast, we find a
positive result for the number of legislators in the upper house ($k$), which is
in line with the mainstream literature (successes = `r as.numeric(binK$statistic)`, trials = `r as.numeric(binK$parameter)`, p~success~ = `r round(as.numeric(binK$estimate), 3)`, 95\% CI = [`r round(as.numeric(binK$conf.int[1]), 3)`; `r round(as.numeric(binK$conf.int[2]), 3)`],
$p$-value = `r round(as.numeric(binK$p.value), 3)`).

@@

We then proceed to the meta-analysis. We matched the house size variables with
our measures of government spending and created a theoretical $3 \times 3$
matrix. Out of the 9 possible variable combinations, we found only 7 in
the article pool. Our sample includes no papers that analyse the relationships
between log($n$) and public expenditure per capita or between $k$ and the
logarithm of public expenditure per capita.

>>>>

[^catarina]: PhD Student, University of California San Diego, <catarinamroman@gmail.com>, <http://catarinaroman.github.io>.

@@

Over the past decades, a large literature has examined the relationship between
legislature size and public expenditure. @weingast1981political provided the
general framework to analyse distributive politics. The authors argue that the
larger the number of legislative districts ($n$), the smaller the share of tax
burden each one will bear ($1/n$), thus legislators have an incentive to
overspend in their districts and transfer the costs to the entire polity. Most
early studies that empirically tested the "law of $1/n$", as the theory is
currently known, indeed found a positive correlation between the number of
legislature seats and different measures of government spending, although the
effect was often limited to one house [e.g., @baqir2002districting;
@gilligan1995deviations; @gilligan2001fiscal]. More recently, the discussion of the "law of $1/n$" has surpassed its original formulation. Specifically, the theory meant to explain distributive behavior of US district legislators under majoritarian electoral rules. It has since then been applied to a number of contexts whose political features do not fit into what @weingast1981political had theorized.

The mechanism behind $1/n$ is incumbents' choice of redistributive strategy to optimize chances of reelection. The _norm of universalism_, by which all legislators pass each other's bills, guarantees that all representatives are allotted an amount of resources to cater projects to their voters. @crowley2019law contests this scenario where coordination costs are minimal, aiming at solving the discrepancies in previous works. The literature finds that a number of players and features can override the $1/n$ effect by posing checks to legislative activity and altering coordination costs. First, shifts in the level of intra or intergovernmental competition based on district homogeneity, supermajority rules, the size of coalitions, and even gerrymandering have been shown to interfere with the effect of chamber size on spending [@bjedov; @crain1999; @crowley2015; @gilligan2006; @lee2015; @mukherjee2003; @pecorino2018]. Second, we must take into account players who function as institutional checks, such as strong executives who take on legislative duties, other deliberative chambers, or spending limits, who also directly influence legislators' access to common pool funds [@bradbury2001legislative; @chen_malhotra_2007; @primo2006stop]. Moreover, @primo2008distributive affirm that, due to spatial spillovers, a
collection of small districts can supply public goods more efficiently than the
central government. The authors conclude that a "reverse law of $1/n$" may hold,
wherein a higher number of legislators in small constituencies decrease the
overall public spending.

Our survey of the scholarship confirms this continuum of positive,
insignificant, and negative results. Out 
of the `r dim(dat)[1]` coefficients
included in our article sample, `r as.numeric(round(prop.table(table(dat$scoefnd))*100, 1)[which(names(prop.table(table(dat$scoefnd)))=='Positive Significant')])`\% of
them are positive and statistically significant, `r as.numeric(round(prop.table(table(dat$scoefnd))*100, 1)[which(names(prop.table(table(dat$scoefnd)))=='Positive Insignificant')])`\%
are positive and statistically insignificant, `r as.numeric(round(prop.table(table(dat$scoefnd))*100, 1)[which(names(prop.table(table(dat$scoefnd)))=='Negative Insignificant')])`\%
are negative and statistically insignificant, and `r as.numeric(round(prop.table(table(dat$scoefnd))*100, 1)[which(names(prop.table(table(dat$scoefnd)))=='Negative Significant')])`\% are
negative and statistically significant. A comprehensive survey and systematic review of the existing evidence may help us reach a
meaningful conclusion about the effect of legislature size on public spending.
Meta-analysis is the most appropriate method for this task. Meta-analysis
combines the outcomes of multiple studies into a single estimation and allows
scholars to draw robust conclusions from the aggregated data
[@cooper2019handbook; @hedges1985statistical]. It can also identify potential
sources of study heterogeneity, enabling researchers to assess threats to
external validity and direct future efforts into more promising areas of
academic inquiry [@doucouliagos2008democracy].

In this letter, we conduct the first meta-analysis that tests the generality of
the "law of $1/n$". We have selected `r length(unique(dat$id))` articles that
use quantitative methods to assess the impact of legislature size over
government spending across several dimensions. We run two sets of models: the
first group uses only the main estimates of each selected paper (`r dim(dat)[1]`),
while the second set includes all coefficients reported in our
sample (`r dim(fulldat)[1]`).\footnote{Although there are `r length(unique(dat$id))`
papers in our review, we include `r dim(dat)[1]` coefficients in the restricted 
sample. This is because `r as.numeric(sum(table(table(dat$id))[-1]))` articles 
report separate estimates for the impact of lower and upper house size on 
government expenditures. In the full model, we add every outcome reported in the 
papers, regardless of whether the coefficient comes from the main tables or from 
robustness checks. We discuss our sampling process in the Methods section and in 
the Supplementary Material.}
Our independent variables consist of three measures, namely the size of the
lower chamber, its natural logarithm, and the number of members
in the upper chamber. We evaluate their effect upon public expenditure per
capita, the natural logarithm of public expenditure per capita, and government
expenditure as a percentage of GDP. We then estimate if the results vary
according to four potential sources of effect heterogeneity.

Aggregate results show that legislative size has no significant impact on
public spending. However, the meta-regressions suggest that our study sample
has high levels of heterogeneity, and effects differ substantially according to
study specifications. While papers that employ
conventional linear regressions often find a positive relation between
legislature size and government budgets, recent studies using modern methods of
causal inference, specially those with regression discontinuity designs,
provide consistent evidence for a negative relation. This goes in contrast with
the original theory and supports the existence of a "reverse law of $1/n$".
Additionally, we find that non-majoritarian voting systems decrease government
spending as a percentage of GDP, which is also evidence against the theoretical
expectations of the "law of $1/n$", and they do not have a relevant impact on
the other measures of public expenditure. However, unicameralism strongly supports the positive effect predicted by the original theory. This result is contradictory to the rest of our findings, even if unicameral cases mostly reflect the very specific framework under which the theory developed (loosely checked local governments). In summary, our analysis does not
provide robust support for the theory as originally conceived, and causal
inference models suggest that larger legislatures are associated with lower
public spending.

@@

We collected the study sample using three criteria. First, the study should
cite \citet{weingast1981political} as their work is foundational to the
distributive politics literature. Second, the study had to use quantitative
methods to estimate the relationship between our variables of
interest.\footnote{As meta-analysis requires a single estimate per observation,
we excluded articles that use interaction terms or quadratic specifications of
our independent variables.} Third, the study should be written in the English
language. We conducted a primary search using Scopus, Microsoft Academic, and
Google Scholar, three large academic databases.\footnote{See the Supplementary
Material for code.} Based on the results obtained, we selected key terms to conduct a broader search of the literature. The same eligibility criteria were applied.

Upon restricting the sample, we identified which were the measurement units most commonly used to translate legislature size and public spending. We found those to be public expenditure as a share of GDP, public expenditure per capita, log public expenditure per capita, lower chamber size, upper chamber size, and log lower chamber size. Log upper chamber size is not a commonly used measurement. Unicameralism is captured by lower chamber size ($n = 7$) and by log lower chamber size ($n = 5$). Since much of the literature dedicated to measuring the effects of bicameralism on this relationship, many articles use both lower and upper chamber sizes as key explanatory variables.

After applying our exclusion criteria, the search produced a dataset of 
`r length(unique(dat$id))` studies as of the 5\textsuperscript{th} of March,
2021. Table \ref{tab:papers} contains the full list of articles from which we
drew data. A PRISMA\footnote{The Preferred Reporting Items for Systematic
Reviews and Meta-Analyses (PRISMA) statement provides a checklist designed
to improve the quality and transparency of study selection processes in
meta-analyses. For more information on the PRISMA framework, see
\citet{liberati2009prisma}.} flow diagram showing the number of resulting
papers after each review step is available in section C.2 of the Supplementary Material.

\footnotesize
\begin{longtable}{>{\raggedright\arraybackslash}p{2.9cm}>{\raggedright\arraybackslash}p{4.5cm}>{\centering\arraybackslash}p{1.3cm}>{\centering\arraybackslash}p{1cm}>{\centering\arraybackslash}p{1cm}>{\centering\arraybackslash}p{1.4cm}>{\centering\arraybackslash}p{2.4cm}}
\caption{Papers included in the meta-analysis, ordered by year of appearance}\\
\toprule
\raggedright Author(s) & \centering Title & \centering Journal & \centering Year & \centering Country & \centering Method & \raggedleft Electoral System
\tabularnewline
\midrule
\endhead
```{r, echo = FALSE, results = 'asis', cache = T}
build_nams <- function(x) {
  x_ <- unlist(strsplit(as.character(x), ' & ', fixed = T, useBytes = T))
  if(length(x_) == 1) return(x_)
  else {
    aux <- x_[1]
      for (i in 2:length(x_))
        if (i == length(x_)){
          aux <- paste(aux, ' \\& \\\\ ', x_[i], sep = '')
        } else {
          aux <- paste(aux, ',\\\\ ', x_[i], sep = '')
        }
  }
  return(paste('\\begin{tabular}[t]{@{}l@{}}', aux,'\\end{tabular}', 
                   sep = ''))
}
aux <- dat %>%
  select(authorCite, title, journalCode, year, locationISO, method, elecsys3) %>%
  unique() %>%
  arrange(year)
for (i in 1:dim(aux)[1]) {
  cat(paste(build_nams(aux$authorCite[i]), ' & ', aux$title[i], ' & ',
      aux$journalCode[i], ' & ', aux$year[i], ' & ', 
      aux$locationISO[i], ' & ', aux$method[i], ' & ', 
      aux$elecsys3[i], ' \\\\ [0.5ex]', sep = ''), '\n')
}
```
\bottomrule
\label{tab:papers}
\begin{minipage}{\textwidth}
\renewcommand{\footnoterule}{}
\vspace{-0.5cm}
\footnotetext{\textbf{Note:} Unpub$=$Unpublished, JPE$=$Journal of Political
Economy, EJPE$=$European Journal of Political Economy, PC$=$Public Choice,
JPubE$=$Journal of Public Economics, JPriE$=$Journal of Private Enterprise,
APSR$=$American Political Science Review, SEJ$=$Southern Economic Journal,
UAR$=$Urban Affairs Review, SCID$=$Studies in Comparative International
Development, SSQ$=$Social Science Quarterly, SPPQ$=$State Politics and Policy
Quarterly, CPS$=$Comparative Political Studies, RivPE$=$Rivista di Politica
Economica, E\&P$=$Economics and Politics, NTJ$=$National Tax Journal.}
\footnotetext{\textbf{Note:} 
OLS$=$Ordinary least squares, IV$=$Instrumental variables, Panel$=$Panel
data/fixed effects, RDD$=$Regression discontinuity design, M$=$Majoritarian,
NM$=$Non-majoritarian (mixed or proportional representation).} 
\footnotetext{\textbf{Note:} Country codes
follow the ISO 3166-1 alpha-3 international standard.} \end{minipage}
\end{longtable}

@@

Regarding the dependent variables included in the sample, `r as.numeric(table(unique(dat[,c('id','depvar2')])$depvar2)[which(names(table(unique(dat[,c('id','depvar2')])$depvar2))=='ExpPC')])` studies employ
public expenditure per capita, `r as.numeric(table(unique(dat[,c('id','depvar2')])$depvar2)[which(names(table(unique(dat[,c('id','depvar2')])$depvar2))=='logExpPC')])` papers use its natural logarithm, and `r as.numeric(table(unique(dat[,c('id','depvar2')])$depvar2)[which(names(table(unique(dat[,c('id','depvar2')])$depvar2))=='PCTGDP')])` of them
analyse the impact of legislature size on public expenditures as a percentage of
GDP. This indicates that the area has refined the original formulation of $1/n$
suggested by \citet{weingast1981political} and tested the impact of larger
legislatures on different measures of government spending. Our independent
variables of interest are, lower chamber size (`r as.numeric(table(dat$indepvar2)[which(names(table(dat$indepvar2))=='N')])`), the natural
logarithm of lower chamber size (`r as.numeric(table(dat$indepvar2)[which(names(table(dat$indepvar2))=='logN')])`), and upper chamber
size (`r as.numeric(table(dat$indepvar2)[which(names(table(dat$indepvar2))=='K')])`).

We also coded four moderators that may help us understand the heterogeneity in
the reported results. We included them in our meta-regressions alongside an
indicator for the type of independent variable used in the original study (lower chamber size,
log of lower chamber size, or upper chamber
size). The additional moderators are: 1) publication year; 2) paper
publication in an academic journal; 3) electoral system; 4) estimation method.
Since the literature on the "law of $1/n$" is notably diverse, we were
restricted to include only the moderators that either refer to important
theoretical questions, such as the effect of the electoral system on public
spending, or to essential characteristics of the publications themselves.
Although more moderators exist in the literature (ie., data aggregation level),
they do not appear as often as required for the meta-regressions. Table
\ref{tab:descriptive} shows the descriptive statistics of the moderator
variables.

@@

```{r, warning=F, message=F, echo = FALSE, cache=TRUE, results='asis'}
fulldat$usemeta2 <- factor(fulldat$usemeta)
levels(fulldat$usemeta2) <- c("Extended Sample", "Main Sample")
aux <- select(fulldat, usemeta2, indepvar2, elecsys2, method,
              year, published) %>%
  rename(`Independent Variables` = indepvar2,
         `Electoral system`      = elecsys2,
         `Estimation method`     = method,
         `Year`                  = year,
         `Published work`        = published)

export2md(descrTable(~.-usemeta2, aux, y = aux$usemeta2,
                        show.p.overall = F, show.all = T),
          caption = "Descriptive Statistics of Moderators",
          format  = "latex")
```

To ensure we do not violate the effect size independence assumption, we use two strategies.
Since most selected articles submit their data to a number of tests, varying models and controls, each pair of variables has more than one effect size. First, to reduce the impact of multicollinearity within the same article,
we estimate the models using two sets of study coefficients. The first group
includes only the most rigorous model from each paper, that is, those estimated
with the largest $n$, most control variables, and fixed effects if the authors
added them. If the article employed a regression discontinuity design, we chose
the coefficient from the optimal bandwidth or from the intermediate one. This
sample encompasses `r dim(dat)[1]` estimates, as `r as.numeric(sum(table(table(dat$id))[-1]))` articles analysed two dependent or
independent variables of interest \citep{baqir1999districts, bjedov2014impact,
bradbury2001legislative, chen_malhotra_2007, crowley2019law,
lee2016supermajority, lee2018court, maldonado2013legislatures, primo2006stop,
ricciuti2003trading}. Our second sample, in contrast, contains all the `r dim(fulldat)[1]` effect sizes reported in the `r length(unique(dat$id))` papers. Here we focus on the results for our restricted sample as we consider them more robust, but the findings are very similar when we use the extended set. We discuss eventual differences in the next section. There is also dependence between studies when more than one article uses the same dataset or source of evidence. In our study, for instance, several papers used US state and municipal data from the Census Bureau and the Book of the States, for the same constituencies, under the same time period. To override dependence between articles, the second strategy we use is employing a multilevel random effects model, grouping the studies that use overlapping data.

@@

The "law of $1/n$" states that more legislators increase government expenditure.
Here we employ three methods to assess the empirical validity of that
relationship. First, we run a binomial one-proportion z-test to determine
whether the study coefficients have a positive or negative sign. Then, we fit 9
random-effect models using the \texttt{meta} \citep{balduzzi2019perform} and the
\texttt{dmetar} \citep{dmetar2019} packages for the \texttt{R} statistical
language \citep{rstats2019}. We estimate the true effect size variance
($\tau^2$) with a Restricted Maximum Likelihood Estimator, which the literature
considers the most precise for continuous dependent variables
\citep{veroniki2016methods}. Lastly, we run a series of meta-regressions to test
possible sources of result heterogeneity. To recapitulate, our independent
variables of interest are lower chamber size, the natural logarithm of
lower chamber size, and upper chamber size. The dependent
variables are public expenditure per capita, the natural logarithm of public
expenditure per capita, and government expenditure as a percentage of GDP. Since
the outcomes have different scales, we treat them separately in our models.

@@

The binomial z-test evaluates whether the coefficient of our independent
variables are positive or negative. The null hypothesis here states that the
sign of the coefficient is equally likely to be positive or negative. We start
with lower house size. Our results indicate that there is no correlation
between the number of legislators in the lower house and public expenditure 
(successes = `r as.numeric(binN$statistic)`, trials = `r as.numeric(binN$parameter)`, p~success~ = `r round(as.numeric(binN$estimate), 3)`, 95\% CI = [`r round(as.numeric(binN$conf.int[1]), 3)`; `r round(as.numeric(binN$conf.int[2]), 3)`],
$p$-value = `r round(as.numeric(binN$p.value), 3)`). Note that the "law of $1/n$" suggests that there is a positive
association between both. The binomial test for the natural logarithm of lower chamber size also shows a
non-statistically significant result (successes = `r as.numeric(binlogN$statistic)`, trials = `r as.numeric(binlogN$parameter)`, p~success~ = `r round(as.numeric(binlogN$estimate), 3)`, 95\% CI = [`r round(as.numeric(binlogN$conf.int[1]), 3)`; `r round(as.numeric(binlogN$conf.int[2]), 3)`],
$p$-value = `r round(as.numeric(binlogN$p.value), 3)`). In contrast, we find a
positive result for the number of legislators in the upper house, which is
in line with the mainstream literature (successes = `r as.numeric(binK$statistic)`, trials = `r as.numeric(binK$parameter)`, p~success~ = `r round(as.numeric(binK$estimate), 3)`, 95\% CI = [`r round(as.numeric(binK$conf.int[1]), 3)`; `r round(as.numeric(binK$conf.int[2]), 3)`],
$p$-value = `r round(as.numeric(binK$p.value), 3)`).

@@

We then proceed to the meta-analysis. We matched the house size variables with
our measures of government spending and created a theoretical $3 \times 3$
matrix. Out of the 9 possible variable combinations, we found only 7 in
the article pool. Our sample includes no papers that analyse the relationships
between the log lower chamber size and public expenditure per capita or between upper chamber size and the
logarithm of public expenditure per capita. We standardized effect sizes by drawing the coefficients and standard errors from the articles. When the latter were not directly available, we used t-statistics to retrieve them.
